---
title: "PolicingPandemic data cleaning and analysis"
author: "Sandhya Kajeepeta"
date: "9/17/2020"
output: html_document
---

#Reading in basic packages
```{r}
library(devtools)
library(tidyverse)
library(readr)
library(nlme)
```

#Read in total arrest data
```{r}
#Read in 2020 data
arrests <- read_csv("./Data/Arrests of interest/2021 update/NYPD_Arrest_Data__Year_to_Date.csv")
arrests$ARREST_DATE <- as.Date(arrests$ARREST_DATE, "%m/%d/%Y")

#look at offense categories
table(arrests$OFNS_DESC)
```

#Restrict data to following offense descriptions: DISORDERLY CONDUCT, CRIMINAL MISCHIEF & RELATED OF, CRIMINAL TRESPASS, OFF. AGNST PUB ORD SENSBLTY &, OTHER STATE LAWS (NON PENAL LA
```{r}
arrests <- arrests %>% filter(OFNS_DESC %in% c("DISORDERLY CONDUCT", "CRIMINAL MISCHIEF & RELATED OF", "CRIMINAL TRESPASS", "OFF. AGNST PUB ORD SENSBLTY &", "OTHER STATE LAWS (NON PENAL LA"))
```


#Restrict "OTHER STATE LAWS (NON PENAL LA" offense category to only those related to public health law
```{r}
oth <- arrests %>% filter(OFNS_DESC == "OTHER STATE LAWS (NON PENAL LA")
oth <- oth %>% filter(PD_DESC == "PUBLIC HEALTH LAW,UNCLASSIFIED")
arrests <- arrests %>% filter(OFNS_DESC != "OTHER STATE LAWS (NON PENAL LA")
arrests <- rbind(arrests, oth)
```


#Restricting to study period of interest
```{r}
arrests <- arrests %>% filter(ARREST_DATE < '2020-05-25')
arrests <- arrests %>% filter(ARREST_DATE > '2020-03-11')
```


#NEIGHBORHOOD ANALYSIS

#Get daily arrest counts for each ZCTA (zip)
```{r}
library(sf)
arrests_sf <- arrests %>%
  mutate_at(vars(X_COORD_CD, Y_COORD_CD), as.numeric) %>%   # coordinates must be numeric
  st_as_sf(
    coords = c("X_COORD_CD", "Y_COORD_CD"),
    agr = "constant",
    crs = 2263,       
    stringsAsFactors = FALSE,
    remove = TRUE)
zcta_sf <- read_sf("./Data/Shapefiles/ZCTAs/nyu_2451_34509.shp") %>%
  st_transform(2263) #read shapefile
arrests_in_zcta <- st_join(arrests_sf, zcta_sf) #join both
arrests_zcta_count <- arrests_in_zcta %>% #assign points to nta polygons
  group_by(ARREST_DATE) %>%
  count(zcta)
colnames(arrests_zcta_count)[colnames(arrests_zcta_count)=="n"] <- "n_arrests" #assign new name 
arrests_zcta_count$geometry <- NULL
#now I have daily counts per ZCTA
```

#Create a list of all zips and all days
##This way I can add 0 values for the zips and days with no arrests
```{r}
allzctas <- unique(arrests_zcta_count$zcta)
alldates <- seq(as.Date("2020-03-12"), as.Date("2020-05-24"), "day")
zipdays <- data.frame(expand.grid(allzctas, alldates))
zipdays$zcta <- as.character(zipdays$Var1)
zipdays$Var1 <- NULL
zipdays$ARREST_DATE <- as.Date(zipdays$Var2)
zipdays$Var2 <- NULL
```

#Join full list of zip days to dataset
```{r}
arrests_zcta_count <- arrests_zcta_count %>% full_join(zipdays, by=c("ARREST_DATE", "zcta"))
#Replace all missing with zero
arrests_zcta_count$n_arrests <- ifelse(is.na(arrests_zcta_count$n_arrests), 0, arrests_zcta_count$n_arrests)
```

#pull in zip racial and socioeconomic demographics
```{r}
#Read in zip-level demographic data
zip <- read_csv("./Data/Neighborhood demographics/ZCTA/ZCTA_ACS_2018.csv")
#delete first row
zip <- zip[-1,]
#Select columns of interest
zip <- zip %>% select(c("ZIP Code Tabulation Area (5-digit)", "Total Population","% Total Population: Black or African American Alone", "% Population Age 18 to 64 for Whom Poverty Status  Is Determined: Living in Poverty"))
names(zip) <- c("zcta","pop_estimate","black","poverty")
#2010 demographic data for sensitivity analysis
zip2010 <- read_csv("./Data/Neighborhood demographics/ZCTA/zipLevelAsthma.csv")
zip2010$zcta <- as.character(zip2010$ZCTA)
zip2010$black_2010 <- zip2010$black*100
zip2010$poverty_2010 <- zip2010$poverty*100
zip2010 <- zip2010 %>% select(c(zcta, black_2010, poverty_2010))
zip <- zip %>% left_join(zip2010, by="zcta")
#read in total zip population data
zippop <- read_csv("./Data/Neighborhood demographics/ZCTA/Pop totals.csv")
#delete first row
zippop <- zippop[-1,]
#zip is last 5 digits of GEO_ID
library(stringr)
zippop$GEO_ID <- str_sub(zippop$GEO_ID, start= -5)
zippop$zcta <- as.character(zippop$GEO_ID)
zippop$pop_estimate_2010 <- as.numeric(zippop$P001001)
#join together
zip <- zip %>% left_join(zippop, by="zcta")
#pull in borough
zipboro <- read_csv("./Data/Neighborhood demographics/ZCTA/zip_boro.csv")
zipboro$zcta <- as.character(zipboro$zcta)
zipboro <- distinct(zipboro)
zip <- zip %>% left_join(zipboro, by="zcta")
```

#Join demographic data with arrest data
```{r}
#Join with arrest counts
arrests_zcta_count <- arrests_zcta_count %>% left_join(zip, by="zcta")
#Recode demographics to numeric and drop any zips with boro=0 (not really in NYC)
arrests_zcta_count$pop_estimate <- as.numeric(arrests_zcta_count$pop_estimate)
arrests_zcta_count$black <- as.numeric(arrests_zcta_count$black)
arrests_zcta_count$poverty <- as.numeric(arrests_zcta_count$poverty)
arrests_zcta_count$pop_estimate_2010 <- as.numeric(arrests_zcta_count$pop_estimate_2010)
arrests_zcta_count$black_2010 <- as.numeric(arrests_zcta_count$black_2010)
arrests_zcta_count$poverty_2010 <- as.numeric(arrests_zcta_count$poverty_2010)
arrests_zcta_count <- arrests_zcta_count %>% filter(!is.na(boro))
#delete unnecessary columns
arrests_zcta_count$GEO_ID <- NULL
arrests_zcta_count$NAME <- NULL
arrests_zcta_count$P001001 <- NULL
#drop any zips with pop < 200
arrests_zcta_count <- arrests_zcta_count %>% filter(pop_estimate > 200)
```

#Standardize % black
```{r}
mean(arrests_zcta_count$black, na.rm=TRUE)
sd(arrests_zcta_count$black, na.rm=TRUE)
arrests_zcta_count$blackz <- (arrests_zcta_count$black-mean(arrests_zcta_count$black, na.rm=TRUE))/sd(arrests_zcta_count$black, na.rm=TRUE)
```

#Standardize % black for sensitivity analysis (2010)
```{r}
mean(arrests_zcta_count$black_2010, na.rm=TRUE)
sd(arrests_zcta_count$black_2010, na.rm=TRUE)
arrests_zcta_count$blackz_2010 <- (arrests_zcta_count$black_2010-mean(arrests_zcta_count$black_2010, na.rm=TRUE))/sd(arrests_zcta_count$black_2010, na.rm=TRUE)
```


#Standardize % poverty
```{r}
mean(arrests_zcta_count$poverty, na.rm=TRUE)
sd(arrests_zcta_count$poverty, na.rm=TRUE)
arrests_zcta_count$povertyz <- (arrests_zcta_count$poverty-mean(arrests_zcta_count$poverty, na.rm=TRUE))/sd(arrests_zcta_count$poverty, na.rm=TRUE)
```

#Standardize % poverty for 2010 sensitivity analysis
```{r}
mean(arrests_zcta_count$poverty_2010, na.rm=TRUE)
sd(arrests_zcta_count$poverty_2010, na.rm=TRUE)
arrests_zcta_count$povertyz_2010 <- (arrests_zcta_count$poverty_2010-mean(arrests_zcta_count$poverty_2010, na.rm=TRUE))/sd(arrests_zcta_count$poverty_2010, na.rm=TRUE)
```

#Aggregate total arrests across dates
```{r}
arrests_zcta_count <- arrests_zcta_count %>% select(zcta, n_arrests, pop_estimate, black, blackz, poverty, povertyz, boro, pop_estimate_2010, blackz_2010, povertyz_2010)
arrests_zcta_count <- arrests_zcta_count %>% group_by(zcta, pop_estimate, black, blackz, poverty, povertyz, boro, pop_estimate_2010, blackz_2010, povertyz_2010) %>% summarise(arrests = sum(n_arrests))
```

#Pull in median non-home dwell time by zip
```{r}
socialDistancing <- read_csv("./Data/Social distancing covariates/socialDistancing2.csv") #read social distancing data
socialDistancing <- select(socialDistancing, zcta, weighted_median_non_home_dwell_time)
socialDistancing$zcta <- as.character(socialDistancing$zcta)
arrests_SD <- arrests_zcta_count %>% select(c(zcta, pop_estimate, black, blackz, poverty, povertyz, boro, arrests, pop_estimate_2010, blackz_2010, povertyz_2010))
arrests_SD$geometry <- NULL
arrests_SD <- left_join(arrests_SD, socialDistancing, by=c("zcta"))
#standardize median non-home dwell time
arrests_SD$weighted_median_non_home_dwell_timez <- (arrests_SD$weighted_median_non_home_dwell_time - mean(arrests_SD$weighted_median_non_home_dwell_time, na.rm=TRUE))/sd(arrests_SD$weighted_median_non_home_dwell_time, na.rm=TRUE)
```

#Pull in 311 social distancing complaint data
```{r}
df311 <- read_csv("./Data/Social distancing covariates/df311.csv")
# pull out all PH related offences in description and create ZCTA counts
df311$Descriptor <- as.factor(df311$Descriptor)
#levels(df311$Descriptor)
sd311 <- filter(df311, grepl("Social Distancing", Descriptor, ignore.case = TRUE))
sd311$date <- sd311$'Created Date'
sd311$date <- as.Date(sd311$date, format = "%m/%d/%Y")
sd311$zcta <- sd311$'Incident Zip'
#Restrict to study period 3/12-5/24
sd311 <- sd311 %>% filter(date < '2020-05-25')
sd311_dayZip <- sd311 %>% 
  group_by(date, zcta) %>% 
  tally()%>%
  rename(n_complaintsSD = n)%>%
  ungroup()
sd311_dayZip$zcta <- as.character(sd311_dayZip$zcta)
#get total complaints in post-lockdown period
sd311_Zip <- sd311_dayZip %>% group_by(zcta) %>% summarise(complaintsSD = sum(n_complaintsSD))
arrests_SD <- left_join(arrests_SD, sd311_Zip, by=c("zcta"))
#replace missing with 0
arrests_SD$complaintsSD <- ifelse(is.na(arrests_SD$complaintsSD), 0, arrests_SD$complaintsSD)
#convert number of complaints to a rate
arrests_SD$complaintsSD_rate <- arrests_SD$complaintsSD/arrests_SD$pop_estimate*100000
arrests_SD$pop_estimate_2010 <- ifelse(arrests_SD$pop_estimate_2010==0, NA, arrests_SD$pop_estimate_2010)
arrests_SD$complaintsSD_rate_2010 <- arrests_SD$complaintsSD/arrests_SD$pop_estimate_2010
#standardize
arrests_SD$complaintsSD_ratez <- (arrests_SD$complaintsSD_rate - mean(arrests_SD$complaintsSD_rate, na.rm=TRUE))/sd(arrests_SD$complaintsSD_rate, na.rm=TRUE)
arrests_SD$complaintsSD_ratez_2010 <- (arrests_SD$complaintsSD_rate_2010 - mean(arrests_SD$complaintsSD_rate_2010, na.rm=TRUE))/sd(arrests_SD$complaintsSD_rate_2010, na.rm=TRUE)
```

#Read in criminal summons data
```{r}
summons <- read_csv("./Data/Summonses/NYPD_Criminal_Court_Summons_Incident_Level_Data__Year_To_Date_.csv")
summons$date <- as.Date(summons$SUMMONS_DATE, format = "%m/%d/%Y")
summons_sf <- summons %>%
  mutate_at(vars(X_COORDINATE_CD, Y_COORDINATE_CD), as.numeric) %>%   # coordinates must be numeric
  st_as_sf(
    coords = c("X_COORDINATE_CD", "Y_COORDINATE_CD"),
    agr = "constant",
    crs = 2263,        
    stringsAsFactors = FALSE,
    remove = TRUE)
zcta_sf <- read_sf("./Data/Shapefiles/ZCTAs/nyu_2451_34509.shp") %>%
  st_transform(2263) #read shapefile
summons_in_zcta <- st_join(summons_sf, zcta_sf) #join both
summons_zcta_count <- summons_in_zcta %>% #assign points to nta polygons
  group_by(date) %>%
  count(zcta)
colnames(summons_zcta_count)[colnames(summons_zcta_count)=="n"] <- "n_summons" #assign new name
summons_zcta_count$geometry <- NULL
#get total complaints in post-lockdown period
summons_zip <- summons_zcta_count %>% group_by(zcta) %>% summarise(summons = sum(n_summons))
arrests_SD <- left_join(arrests_SD, summons_zip, by=c("zcta"))
#replace missing with 0
arrests_SD$summons <- ifelse(is.na(arrests_SD$summons), 0, arrests_SD$summons)
```

#Unadjusted associations with boro fixed effects
##Run Poisson regression - by percent_black (standardized)
```{r}
m6 <- glm(formula = arrests ~ blackz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m6)
exp(m6$coefficients["blackz"])
exp(confint(m6))
```

###2010 sensitivity analysis
```{r}
m7 <- glm(formula = arrests ~ blackz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m7)
exp(m7$coefficients["blackz_2010"])
exp(confint(m7))
```

##Run Poisson regression - by percent_poverty (standardized)
```{r}
m8 <- glm(formula = arrests ~ povertyz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m8)
exp(m8$coefficients["povertyz"])
exp(confint(m8))
```

###2010 sensitivity analysis
```{r}
m9 <- glm(formula = arrests ~ povertyz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m9)
exp(m9$coefficients["povertyz_2010"])
exp(confint(m9))
```

#Adjusted associations between % black and poverty with arrests
##Run Poisson regression - by percent_black (standardized)
```{r}
m10 <- glm(formula = arrests ~ blackz + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m10)
exp(m10$coefficients["blackz"])
exp(confint(m10))
```

###2010 sensitivity analysis
```{r}
m11 <- glm(formula = arrests ~ blackz_2010 + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez_2010 + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m11)
exp(m11$coefficients["blackz_2010"])
exp(confint(m11))
```

##Run Poisson regression - by percent_poverty (standardized)
```{r}
m12 <- glm(formula = arrests ~ povertyz + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m12)
exp(m12$coefficients["povertyz"])
exp(confint(m12))
```

###2010 sensitivity analysis
```{r}
m13 <- glm(formula = arrests ~ povertyz_2010 + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez_2010 + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m13)
exp(m13$coefficients["povertyz_2010"])
exp(confint(m13))
```

#Crude and adjusted associations with summonses
##Remove Staten Island because no zips in SI had summonses
```{r}
arrests_SD2 <- arrests_SD %>% filter(boro != "Staten")
```

##Crude
###Run Poisson regression - by percent_black (standardized)
```{r}
m14 <- glm(formula = summons ~ blackz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m14)
exp(m14$coefficients["blackz"])
exp(confint(m14))
```

####2010 sensitivity analysis
```{r}
m15 <- glm(formula = summons ~ blackz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m15)
exp(m15$coefficients["blackz_2010"])
exp(confint(m15))
```

##Run Poisson regression - by percent_poverty (standardized)
```{r}
m16 <- glm(formula = summons ~ povertyz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m16)
exp(m16$coefficients["povertyz"])
exp(confint(m16))
```

####2010 sensitivity
```{r}
m17 <- glm(formula = summons ~ povertyz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m17)
exp(m17$coefficients["povertyz_2010"])
exp(confint(m17))
```

##Adjusted
###Run Poisson regression - by percent_black (standardized)
```{r}
m18 <- glm(formula = summons ~ blackz + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m18)
exp(m18$coefficients["blackz"])
exp(confint(m18))
```

###2010 sensitivity analysis
```{r}
m19 <- glm(formula = summons ~ blackz_2010 + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez_2010 + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m19)
exp(m19$coefficients["blackz_2010"])
exp(confint(m19))
```

###Run Poisson regression - by percent_poverty (standardized)
```{r}
m20 <- glm(formula = summons ~ povertyz + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m20)
exp(m20$coefficients["povertyz"])
exp(confint(m20))
```

####2010 sensitivity analysis
```{r}
m21 <- glm(formula = summons ~ povertyz_2010 + boro + weighted_median_non_home_dwell_timez + complaintsSD_ratez_2010 + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m21)
exp(m21$coefficients["povertyz_2010"])
exp(confint(m21))
```

#Read in stop and frisk spatial data
```{r}
sqf <- read_csv("./Data/SQF2011.csv")
summary(sqf)
sqf$datestop <- str_sub(sqf$datestop, end=-5)
sqf$day <- str_sub(sqf$datestop, start=-2)
sqf$month <- str_sub(sqf$datestop, end=-3)
sqf$date <- as.Date(ISOdate(sqf$year,sqf$month, sqf$day))
sqf <- sqf %>% filter(!is.na(xcoord) & !is.na(ycoord))
sqf_sf <- sqf %>%
  mutate_at(vars(xcoord, ycoord), as.numeric) %>%   # coordinates must be numeric
  st_as_sf(
    coords = c("xcoord", "ycoord"),
    agr = "constant",
    crs = 2263,        
    stringsAsFactors = FALSE,
    remove = TRUE)
zcta_sf <- read_sf("./Data/Shapefiles/ZCTAs/nyu_2451_34509.shp") %>%
  st_transform(2263) #read shapefile
sqf_in_zip <- st_join(sqf_sf, zcta_sf) #join both
sqf_zip_count <- sqf_in_zip %>% #assign points to nta polygons
  group_by(date) %>%
  count(zcta)
colnames(sqf_zip_count)[colnames(sqf_zip_count)=="n"] <- "n_arrests" #assign new name 
sqf_zip_count$geometry <- NULL
#now I have daily counts per zip
```

#Sum to get total SQF incidents in 2011 per zip
```{r}
sqf_zip_count <- sqf_zip_count %>% left_join(zip, by="zcta") %>% select(zcta, date, n_arrests)
mapsqf <- sqf_zip_count %>% group_by(zcta) %>% summarise(sqf = sum(n_arrests))
```

#Joining stop and frisk data
```{r}
arrests_SD <- arrests_SD %>% left_join(mapsqf, by=c("zcta"))
#convert to rate
arrests_SD$sqfrate <- arrests_SD$sqf/arrests_SD$pop_estimate_2010*100000
#standardize sqf rate
arrests_SD$sqfratez <- (arrests_SD$sqfrate - mean(arrests_SD$sqfrate, na.rm=TRUE))/sd(arrests_SD$sqfrate, na.rm=TRUE)
```

#Individual associations with arrest rate (quasi-Poisson regression)
##blackz
```{r}
m22 <- glm(formula = arrests ~ blackz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m22)
exp(m22$coefficients["blackz"])
exp(confint(m22))
```

##2010 sensitivity analysis
```{r}
m23 <- glm(formula = arrests ~ blackz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m23)
exp(m23$coefficients["blackz_2010"])
exp(confint(m23))
```

##povertyz
```{r}
m24 <- glm(formula = arrests ~ povertyz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m24)
exp(m24$coefficients["povertyz"])
exp(confint(m24))
```

##2010 sensitivity analysis
```{r}
m25 <- glm(formula = arrests ~ povertyz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m25)
exp(m25$coefficients["povertyz_2010"])
exp(confint(m25))
```

##weighted_median_non_home_dwell_timez
```{r}
m26 <- glm(formula = arrests ~ weighted_median_non_home_dwell_timez + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m26)
exp(m26$coefficients["weighted_median_non_home_dwell_timez"])
exp(confint(m26))
```

##2010 sensitivity analysis
```{r}
m27 <- glm(formula = arrests ~ weighted_median_non_home_dwell_timez + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m27)
exp(m27$coefficients["weighted_median_non_home_dwell_timez"])
exp(confint(m27))
```

##311 complaints
```{r}
m28 <- glm(formula = arrests ~ complaintsSD_ratez + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m28)
exp(m28$coefficients["complaintsSD_ratez"])
exp(confint(m28))
```

##2010 sensitivity analysis
```{r}
m29 <- glm(formula = arrests ~ complaintsSD_ratez_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m29)
exp(m29$coefficients["complaintsSD_ratez_2010"])
exp(confint(m29))
```

##2011 SQF arrests
```{r}
m30 <- glm(formula = arrests ~ sqfratez + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD)
summary(m30)
exp(m30$coefficients["sqfratez"])
exp(confint(m30))
```

##2010 sensitivity analysis
```{r}
m31 <- glm(formula = arrests ~ sqfratez + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD)
summary(m31)
exp(m31$coefficients["sqfratez"])
exp(confint(m31))
```

#Individual associations with summons rate (quasi-Poisson regression)
##Drop Staten Island
```{r}
arrests_SD2 <- arrests_SD %>% filter(boro != "Staten")
```

##blackz
```{r}
m32 <- glm(formula = summons ~ blackz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m32)
exp(m32$coefficients["blackz"])
exp(confint(m32))
```

##2010 sensitivity analysis
```{r}
m33 <- glm(formula = summons ~ blackz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m33)
exp(m33$coefficients["blackz_2010"])
exp(confint(m33))
```

##povertyz
```{r}
m34 <- glm(formula = summons ~ povertyz + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m34)
exp(m34$coefficients["povertyz"])
exp(confint(m34))
```

##2010 sensitivity analysis
```{r}
m35 <- glm(formula = summons ~ povertyz_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m35)
exp(m35$coefficients["povertyz_2010"])
exp(confint(m35))
```

##weighted_median_non_home_dwell_timez
```{r}
m36 <- glm(formula = summons ~ weighted_median_non_home_dwell_timez + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m36)
exp(m36$coefficients["weighted_median_non_home_dwell_timez"])
exp(confint(m36))
```

##2010 sensitivity analysis
```{r}
m37 <- glm(formula = summons ~ weighted_median_non_home_dwell_timez + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m37)
exp(m37$coefficients["weighted_median_non_home_dwell_timez"])
exp(confint(m37))
```

##311 complaints
```{r}
m38 <- glm(formula = summons ~ complaintsSD_ratez + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m38)
exp(m38$coefficients["complaintsSD_ratez"])
exp(confint(m38))
```

##2010 sensitivity analysis
```{r}
m39 <- glm(formula = summons ~ complaintsSD_ratez_2010 + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m39)
exp(m39$coefficients["complaintsSD_ratez_2010"])
exp(confint(m39))
```

##2011 SQF arrests
```{r}
m40 <- glm(formula = summons ~ sqfratez + boro + offset(log(pop_estimate)), family=quasipoisson, data=arrests_SD2)
summary(m40)
exp(m40$coefficients["sqfratez"])
exp(confint(m40))
```

##2010 sensitivity analysis
```{r}
m41 <- glm(formula = summons ~ sqfratez + boro + offset(log(pop_estimate_2010)), family=quasipoisson, data=arrests_SD2)
summary(m41)
exp(m41$coefficients["sqfratez"])
exp(confint(m41))
```

#Code to create Figure

#load in necessary packages and prep dataframe
```{r}
library(readr)
library(sf)
library(sp)
library(scales)
library(ggplot2)
library(ggthemes)
library(grid)
library(cowplot)
library(tidyverse)
library(gtools)
library(tigris)
options(scipen = 999)
arrests_SD <- as.data.frame(arrests_SD)
arrests_SD2 <- arrests_SD %>% 
  mutate(arrestRate = (arrests/pop_estimate)*100000, summonsRate = (summons/pop_estimate)*100000) %>% 
  mutate(across(c(arrestRate, 
                  black, 
                  poverty, 
                  weighted_median_non_home_dwell_time, 
                  complaintsSD_rate,
                  sqfrate), 
                list(cut = ~quantcut(., 5, labels = c("1", "2", "3", "4", "5")))
                  )
  ) 
nyc.df <- merge(zcta_sf, arrests_SD2, by.y="zcta", all=FALSE)
nyc.df$Borough <- ifelse(nyc.df$boro=="Staten", "Staten Island", nyc.df$boro)
cbPalette <- c("#b3cde0", "#6497b1", "#005b96", "#03396c", "#011f4b", "#011f4b")
```

#Arrests
## Get more geographies
```{r}
st_erase = function(x, y) st_difference(x, st_union(st_combine(y)))
### Import census geographies ####
## Import water
nyc_water <- suppressMessages(rbind(
  area_water("NY", "New York", class = "sf"),
  area_water("NY", "Kings", class = "sf"),
  area_water("NY", "Queens", class = "sf"),
  area_water("NY", "Bronx", class = "sf"),
  area_water("NY", "Richmond", class = "sf"),
  area_water("NY", "Nassau", class = "sf"),
  area_water("NY", "Westchester", class = "sf"),
  area_water("NJ", "Bergen", class = "sf"),
  area_water("NJ", "Hudson", class = "sf")) %>% 
  st_transform(26918) %>% 
  st_union())
nyc_surrounding <- states(cb = TRUE, class = "sf")
nyc_surrounding <- nyc_surrounding %>% 
  filter(NAME %in% c("New York", "New Jersey"))
```
#Arrest Figures
## Map
```{r}
#add standard cartographic elements
#add land around nyc
#tigris package
#get tiger line get nyc and nj state boundaries
library(ggspatial)
arrest_map <- ggplot(data = nyc.df, aes(geometry = geometry, fill = arrestRate_cut)) + 
  geom_sf(data = nyc_surrounding, fill = "grey92", size = 0.1, color = "transparent") +
  geom_sf(data = nyc_water, fill = "white", size = 0.1, color = "transparent") +
  geom_sf(size = 0.1, color = "white") +
  annotation_north_arrow(which_north = "true", 
                         location = "br", 
                         width = unit(0.5, "cm"), 
                         height = unit(0.5, "cm"), 
                         style = north_arrow_orienteering(text_size = 6) ) +
  annotation_scale(location = "bl", pad_x = unit(7.2, "cm"), height = unit(.1, "cm")) +
  coord_sf(xlim = st_bbox(nyc.df)[c(1, 3)], ylim = st_bbox(nyc.df)[c(2, 4)]) +
  theme_bw() +
  scale_fill_manual(values=cbPalette)+
    theme(plot.title = element_text(size = 10), axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        legend.position = c(.12, .9),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.key.size = unit(0.25, "cm"),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank()) +
  labs(fill = "Quintile") +
  guides(fill = guide_legend(label.position = "bottom", title.position = "top")) +
  xlab("") +
  ylab("") +
  ggtitle('Public health and miscellaneous arrest rate')
arrest_map
```
## Print
```{r}
png("/Users/sk4538/Sync/Mass Incarceration and Public Health/COVID and arrests/Graphs/2021 update/Fig 1 Arrest Rate.png", width = 5, height = 5, units = "in", res = 500)
arrest_map 
dev.off()
```

#Black
## Map
```{r}
black_map <- ggplot(data = nyc.df, aes(geometry = geometry, fill = black_cut)) + 
  geom_sf(data = nyc_surrounding, fill = "grey92", size = 0.1, color = "transparent") +
  geom_sf(data = nyc_water, fill = "white", size = 0.1, color = "transparent") +
  geom_sf(size = 0.1, color = "white") +
  coord_sf(xlim = st_bbox(nyc.df)[c(1, 3)], ylim = st_bbox(nyc.df)[c(2, 4)]) +
  theme_bw() +
  scale_fill_manual(values=cbPalette) +
  theme(plot.title = element_text(size = 10),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        panel.grid = element_blank(),
        panel.border = element_blank())+
  xlab("") +
  ylab("") +
  labs(fill = "Quintile") + 
  ggtitle('Percentage of Black residents') +
  guides(fill = guide_legend(label.position = "bottom", title.position = "top"))
```

## Scatter
```{r}
black_scatter <- ggplot(nyc.df, aes(y = black, 
                          x = arrestRate, 
                          shape = Borough)) +
  geom_point(size = 1) +
  theme_bw() +
  theme(
        panel.grid = element_blank() ,
        axis.title.x = element_text(size = 8, face = "italic"),
        axis.text = element_text(size = 8),
        plot.background = element_rect(fill = "transparent",colour = NA)) +
  xlab("Public health arrest rate per 100,000") +
  ylab("") +
  labs(shape = "Borough") + 
  geom_smooth(method='glm', method.args = list(family = quasipoisson), na.rm = TRUE, fullrange= TRUE,
              aes(group=1),colour="#005b96", size = .75)  +
  guides(shape = guide_legend(label.position = "bottom", title.position = "top"))
```

# Poverty
## Map
```{r}
poor_map <- ggplot(data = nyc.df, aes(geometry = geometry, fill = poverty_cut)) + 
  geom_sf(data = nyc_surrounding, fill = "grey92", size = 0.1, color = "transparent") +
  geom_sf(data = nyc_water, fill = "white", size = 0.1, color = "transparent") +
  geom_sf(size = 0.1, color = "white") +
  coord_sf(xlim = st_bbox(nyc.df)[c(1, 3)], ylim = st_bbox(nyc.df)[c(2, 4)]) +
  theme_bw() +
  scale_fill_manual(values=cbPalette) +
  theme(plot.title = element_text(size = 10),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        panel.grid = element_blank(),
        panel.border = element_blank())+
  xlab("") +
  ylab("") +
  labs(fill = "Quintile") +   
  ggtitle('Percentage of residents below the federal poverty line') +
  guides(fill = guide_legend(label.position = "bottom", title.position = "top"))
```

## Scatter

```{r}
poor_scatter <- ggplot(nyc.df, aes(y = poverty, 
                        x = arrestRate, 
                        shape = Borough))+
  geom_point(size = 1) +
  theme_bw() +
  theme(
        panel.grid = element_blank(),
        plot.background = element_rect(fill = "transparent",colour = NA),
        axis.text = element_text(size = 8)) +
  xlab("") +
  ylab("") +
    labs(shape = "Borough") + 
  geom_smooth(method='glm', method.args = list(family = quasipoisson), na.rm = TRUE, fullrange= TRUE,
              aes(group=1),colour="#005b96", size = .75)  +
  guides(shape = guide_legend(label.position = "bottom", title.position = "top"))                  
```

# Dwell time
## Map
```{r}
dwell.data <- nyc.df %>% 
  filter(!is.na(weighted_median_non_home_dwell_time))
dwell_map <- ggplot(data = dwell.data, aes(geometry = geometry, fill = weighted_median_non_home_dwell_time_cut)) + 
  geom_sf(data = nyc_surrounding, fill = "grey92", size = 0.1, color = "transparent") +
  geom_sf(data = nyc_water, fill = "white", size = 0.1, color = "transparent") +
  geom_sf(size = 0.1, color = "white") +
  coord_sf(xlim = st_bbox(nyc.df)[c(1, 3)], ylim = st_bbox(nyc.df)[c(2, 4)]) +
  theme_bw() +
  scale_fill_manual(values=cbPalette) +
  theme(plot.title = element_text(size = 10),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        panel.grid = element_blank(),
        panel.border = element_blank())+
  xlab("") +
  ylab("") +
  labs(fill = "Quintile") + 
  ggtitle('Weighted median non-home dwell time (minutes)') +
  guides(fill = guide_legend(label.position = "bottom", title.position = "top"))
```

## Scatter
```{r}
dwell_scatter <- ggplot(nyc.df, aes(y = weighted_median_non_home_dwell_time, 
                          x = arrestRate, 
                          shape = Borough))+
  geom_point(size = 1) +
  theme_bw() +
  theme(
        panel.grid = element_blank(),
        plot.background = element_rect(fill = "transparent",colour = NA),
        axis.text = element_text(size = 8)) +
  xlab("") +
  ylab("")  +     
    labs(shape = "Borough") + 
  geom_smooth(method='glm', method.args = list(family = quasipoisson), na.rm = TRUE, fullrange= TRUE,
              aes(group=1),colour="#005b96", size = .75)  +
  guides(shape = guide_legend(label.position = "bottom", title.position = "top"))
```

# Social distancing
## Map

```{r}
socdis_map <- ggplot(data = nyc.df, aes(geometry = geometry, fill = complaintsSD_rate_cut)) + 
  geom_sf(data = nyc_surrounding, fill = "grey92", size = 0.1, color = "transparent") +
  geom_sf(data = nyc_water, fill = "white", size = 0.1, color = "transparent") +
  geom_sf(size = 0.1, color = "white") +
  coord_sf(xlim = st_bbox(nyc.df)[c(1, 3)], ylim = st_bbox(nyc.df)[c(2, 4)]) +
  theme_bw() +
  scale_fill_manual(values=cbPalette) +
  theme(plot.title = element_text(size = 10),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        panel.grid = element_blank(),
        panel.border = element_blank())+
  xlab("") +
  ylab("") +
  labs(fill = "Quintile") + 
  ggtitle('Rate of social distancing 311 complaints per 100,000') +
  guides(fill = guide_legend(label.position = "bottom", title.position = "top"))
```

## Scatter

```{r}
socdis_scatter <- ggplot(nyc.df, aes(y = complaintsSD_rate, 
                           x = arrestRate, 
                           shape = Borough))+
  geom_point(size = 1) +
  theme_bw() +
  theme(
        panel.grid = element_blank(),
        plot.background = element_rect(fill = "transparent",colour = NA),
        axis.text = element_text(size = 8)) +
  xlab("") +
  ylab("") +      
    labs(shape = "Borough") + 
  geom_smooth(method='glm', method.args = list(family = quasipoisson), na.rm = TRUE, fullrange= TRUE,
              aes(group=1),colour="#005b96", size = .75) +
  guides(shape = guide_legend(label.position = "bottom", title.position = "top"))
```


# Stop and frisk
## Map

```{r}
stop_map <- ggplot(data = nyc.df, aes(geometry = geometry, fill = sqfrate_cut)) + 
  geom_sf(data = nyc_surrounding, fill = "grey92", size = 0.1, color = "transparent") +
  geom_sf(data = nyc_water, fill = "white", size = 0.1, color = "transparent") +
  geom_sf(size = 0.1, color = "white") +
  coord_sf(xlim = st_bbox(nyc.df)[c(1, 3)], ylim = st_bbox(nyc.df)[c(2, 4)]) +
  theme_bw() +
  scale_fill_manual(values=cbPalette) +
  theme(plot.title = element_text(size = 10),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        panel.grid = element_blank(),
        panel.border = element_blank())+
  xlab("") +
  ylab("") +
  labs(fill = "Quintile") + 
  ggtitle('2011 rate of stop-and-frisk incidents per 100,000') +
  guides(fill = guide_legend(label.position = "bottom", title.position = "top"))
```

## Scatter

```{r}
stop_scatter <- ggplot(nyc.df, aes(y = sqfrate, 
                            x = arrestRate, 
                            shape = Borough))+
  geom_point(size = 1) +
  theme_bw() +
  theme(
        panel.grid = element_blank(),
        plot.background = element_rect(fill = "transparent",colour = NA),
        axis.text = element_text(size = 8)) +
  xlab("") +
  ylab("") +
    labs(shape = "Borough") + 
  geom_smooth(method='glm', method.args = list(family = quasipoisson), na.rm = TRUE, fullrange= TRUE,
              aes(group=1),colour="#005b96", size = .75)  +
  guides(shape = guide_legend(label.position = "bottom", title.position = "top"))
```

# Print grid map
```{r}
library(patchwork)
png("/Users/sk4538/Sync/Mass Incarceration and Public Health/COVID and arrests/Graphs/2021 update/Fig 2 Arrest Maps with Scatter.png", width = 5, height = 11, units = "in", res = 500)
wrap_plots(black_map, 
           black_scatter, 
           poor_map, 
           poor_scatter, 
           dwell_map, 
           dwell_scatter, 
           socdis_map, 
           socdis_scatter, 
           stop_map, 
           stop_scatter, 
          ncol = 2) +
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom",
        legend.key.size = unit(.25, "cm"),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 8))
dev.off()
```

